Paper_analyses

### 2021-08-25 IAPS_PREPROCESSING_2021_1.Rmd
fixed import biopac

unique(db_leda_bio$trigger)

@@

# move counter to 1
range(db_leda_bio$Event.Nr-1)
range(db_leda_bio$Event.Nr)
trigger$Event.Nr<- NULL

db_leda_bio$order <- db_leda_bio$Event.Nr-1
db_leda_bio$trigger<- NULL

@@

db_leda_bio$order
db_leda_bio<- left_join(db_leda_bio, trigger)

@@

newnames<- c("Event.Nr", paste0("BIO_", paste0(leda_bioames[2:21])))

newnames
db_leda_bio_backup<- db_leda_bio
names(db_leda_bio) <- newnames

@@

db_leda_bio$ssid <- db_leda_bio$BIO_ssid

db_leda_bio$BIO_ssid<-NULL

tmp.df4_sum_full_bio<- left_join(tmp.df4_sum_full,  db_leda_bio)

@@

>>>>

# unique(db_leda_bio$trigger)

@@

# move counter to 1
range(db_leda_bio$Event.Nr-1)
# range(db_leda_bio$Event.Nr)
# trigger$Event.Nr<- NULL

db_leda_bio$order <- db_leda_bio$Event.Nr-1
# db_leda_bio$trigger<- NULL

@@

db_leda_bio$order
# db_345_355$order

trigger<- db_345_355 %>%
  group_by(order,trigger, tNo)%>%
  summarise_at(c('ssid'), mean, na.rm = TRUE)
  # select(db_345_355, c(trigger, tNo, order))

  trigger$ssid<- NULL

  db_leda_bio<- left_join(db_leda_bio, trigger)

@@

leda_bioames
newnames<- c("Event.Nr", paste0("BIO_", paste(leda_bioames[2:16])),"BIO_Event.NID","BIO_filename"  ,"ssid","order","trigger")

newnames

db_leda_bio_backup<- db_leda_bio

colnames(db_leda_bio_backup)

names(db_leda_bio) <- newnames

# db_leda_bio$ssid <- db_leda_bio$BIO_ssid

# db_leda_bio$BIO_ssid<-NULL

@@

db_leda_bio$ssid<- as.character(db_leda_bio$ssid)

# db_leda_bio$order<- db_leda_bio$BIO_order

unique(tmp.df4_sum_full$Event.Nr)

db_leda_bio$BIO_Event.NID<- NULL
db_leda_bio$BIO_filename<- NULL

tmp.df4_sum_full_bio<- left_join(tmp.df4_sum_full,  db_leda_bio, by = c("ssid", "order"))

@@

write_csv(db_leda_bio, "db_leda_bio_346_347_ledagsr.csv")

write_csv(db_leda_bio, "db_leda_bio_346_355_ledagsr.csv")
```

### 2021-08-25 Paper_Analyses_subj_obje_arousal.Rmd
fixed import biopac

```{r}
participants_demog <- db_full4new_stim_screen_pupil_nopract %>%
  subset(Group == "NT")%>%
  group_by(ssid, Gender)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

>>>>

```{r}
# even though it says no pratice I actually kept the pratice
db_full4new_stim_screen_pupil_nopract$tNo

library(readr)
db_345_355 <- read_csv("tmp.df4_sum_full_bio_hr_self_parsed_345_356.csv")
View(db_345_355)

colnames(db_full4new_stim_screen_pupil_nopract)

participants_demog <- db_full4new_stim_screen_pupil_nopract %>%
  subset(Group == "NT")%>%
  group_by(ssid, Gender)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)
